A new method cluster Detection from three-dimensional weak lensing mass map

### 2021-01-18 doc/paper_ms_method_HSCY1/ms.tex
add citation for original paper for 3Ddet

On the other hand, we can directly reconstruct three-dimensional ($3$-D) mass
maps taking advantage of photometric redshift (photo-$z$) information
\citep{LSS-massMap-Wiener-Simon2009,WL-massMap-VanderPlas2011}; however, these
methods either do not have enough spatial resolution to identify clusters, or
they suffer from smearing along the line of sight direction, which need to be
overcome for practical searches of clusters in 3D mass maps.  Alternatively,
\citet{WL-clusDet-Hennawi2005} propose to perform a maximum-likelihood
detection of clusters, by convolving tomographic shear measurements with $3$-D
filters that match the tangential shears induced by multi-scale NFW halos,
without fully reconstruct the $3$-D mass maps.

>>>>

On the other hand, we can directly reconstruct three-dimensional ($3$-D) mass
maps taking advantage of photometric redshift (photo-$z$) information
\citep{massMap3D-Hu2002,massMap3D-Bacon2003,LSS-massMap-Wiener-Simon2009,WL-massMap-VanderPlas2011};
however, these methods either do not have enough spatial resolution to identify
clusters, or they suffer from smearing along the line of sight direction, which
need to be overcome for practical searches of clusters in 3D mass maps.
Alternatively, \citet{WL-clusDet-Hennawi2005} propose to perform a
maximum-likelihood detection of clusters, by convolving tomographic shear
measurements with $3$-D filters that match the tangential shears induced by
multi-scale NFW halos, without fully reconstruct the $3$-D mass maps.
